### 2012-06-21 inst/examples/criticaltransition.Rmd
criticaltransition with warning signals, graph fixed

``` {r summaryplot}
signals <- melt(data.frame(var=var_tau$V1, acor=acor_tau$V1, m=m$V1))
ggplot(signals) + geom_density(aes(value)) + facet_wrap(~variable)
````

>>>>

``` {r summaryplot}
signals <- melt(data.frame(var=var_tau$V1, acor=acor_tau$V1, m=m$V1))
ggplot(signals) + geom_histogram(aes(value)) + facet_wrap(~variable, scales="free")
````

### 2012-06-21 inst/examples/value_of_information.Rmd
criticaltransition with warning signals, graph fixed

``` {r sethiplots, dependson="runall"}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, det = det$D[,1], g = g$D[,1], m = m$D[,1], gm = gm$D[,1], gi = gi$D[,1], gmi = gmi$D[,1]), id = "stock")
ggplot(policy) + geom_point(aes(stock, stock-x_grid[value], color=variable)) + ylab("escapement") 
ggplot(policy) + geom_smooth(aes(stock, stock-x_grid[value], color=variable))+ ylab("escapement")

value <- melt(data.frame(stock = x_grid, det=det$V, g = g$V, m = m$V, gm = gm$V, gi = gi$V, gmi = gmi$V), id = "stock")
ggplot(value) + geom_point(aes(stock, value, color=variable)) + ylab("Net Present Value")
ggplot(value) + geom_smooth(aes(stock, value, color=variable)) + ylab("Net Present Value")
````

@@

``` {r simfn} 
simulatereps <- function(opt, true_g, true_m, true_i){
  z_g <- function() rlnorm(1,  0, true_g)
  z_m <- function() rlnorm(1,  0, true_m) 
  z_i <- function() rlnorm(1,  0, true_i)

@@

``` {r biblio, echo=FALSE, results="asis"}
print(knitcitations::bibliography(), "html")
````

>>>>

``` {r sethiplots, dependson="runall"}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, det = det$D[,1], g = g$D[,1], m = m$D[,1], i=i$D[,1], gm = gm$D[,1], gi = gi$D[,1], gmi = gmi$D[,1]), id = "stock")
ggplot(policy) + geom_point(aes(stock, stock-x_grid[value], color=variable)) + ylab("escapement") 
ggplot(policy) + geom_smooth(aes(stock, stock-x_grid[value], color=variable))+ ylab("escapement")

value <- melt(data.frame(stock = x_grid, det=det$V, g = g$V, m = m$V, i=i$V, gm = gm$V, gi = gi$V, gmi = gmi$V), id = "stock")
ggplot(value) + geom_point(aes(stock, value, color=variable)) + ylab("Net Present Value")
ggplot(value) + geom_smooth(aes(stock, value, color=variable)) + ylab("Net Present Value")
````

@@

``` {r simfn} 
simulatereps <- function(opt, true_g, true_m, true_i){
  z_g <- function() rnorm(1,  0, true_g)
  z_m <- function() rnorm(1,  0, true_m) 
  z_i <- function() rnorm(1,  0, true_i)

@@

``` {r biblio, echo=FALSE, results="asis"}
knitcitations::bibliography("html")
````

### 2012-06-21 inst/examples/voi_sethi_parameters.Rmd
criticaltransition with warning signals, graph fixed

`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, cache.path="value_of_information/" or`

@@

``` {r sethiplots, dependson="runall"}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, det = det$D[,1], 
               g = g$D[,1], m = m$D[,1], i= m$D[,i], 
               gm = gm$D[,1], gi = gi$D[,1], gmi = gmi$D[,1]), 
               id = "stock")

@@

``` {r biblio, echo=FALSE, results="asis"}
print(knitcitations::bibliography(), "html")
`

>>>>

@@

``` {r sethiplots, dependson="runall"}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, det = det$D[,1], 
               g = g$D[,1], m = m$D[,1], i= m$D[,1], 
               gm = gm$D[,1], gi = gi$D[,1], gmi = gmi$D[,1]), 
               id = "stock")

@@

``` {r biblio, echo=FALSE, results="asis"}
knitcitations::bibliography("html")
````
